---
title: "simpleRegress"
author: "Gloria Jones"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I'm going to try to find the model length of the bear based on chest size.  


```{r}
myheadlen<- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(myheadlen)
summary.lm(myheadlen)
```
  
I have two models simp and mycehst, it appears the second model (mycehst) looks better than the first model(simp) because it explains the error more and the residual standard error is smaller. The first model was using neck, the adjusted r square was 0.747 and the residual standard error was 5.376. In the second model it was using the adjusted r square 0.786 and the residual standard error is 4.939.    
  
  
```{r}
myheadw<- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(myheadw)
summary.lm(myheadw)
```
  
The model myheadw the adjusted r square went down and the residual standard error has gone up.  
  
  
```{r}
myheadlen<- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(myheadlen)
summary.lm(myheadlen)
```

In the model myheadln the adjusted r square is 0.843 and the residual standard error is 4.235. Compared to all the other models, myheadln model shows a batter prediction so far.  
  






